Sample-Based Determination of Angular Observables

### 2014-06-25 draft.tex
Comments and corrections on appendices

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sense that \fred{What are the upper limits? $\pi$ or $2 \pi$? Not consistent with section I and II. I think it would be fair to talk about the dual basis already there.}
\begin{equation}
    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
\end{aligned}
\end{equation}

@@

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.
The decay width is
\begin{equation}
    \Gamma = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
\end{aligned}
\end{equation}
(Note here the notation, where indices with an \emph{i} arise only from S-wave/P-wave interference.)
In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = J_i(q^2) / \Gamma$.\\

@@

The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, with $P,P_1,P_2$ pseudoscalar mesons,
and $\ell_1$, $\bar\ell_2$ charge or neutral leptons, includes decays
such as e.g. $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
Their PDFs can generally be written as \cite{Lee:1992ih}
\begin{equation}
    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
\end{equation}
where
\begin{equation}
\begin{aligned}
    f_1 & = 1\,,              &
    f_2 & = \cos 2\theta_1\,, &
    f_6 & = \cos  \theta_1\,, \\
    f_3 & = \sin^2\theta_1 \cos 2\phi\,,&
    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
    f_5 & = \sin  \theta_1 \cos  \phi\,,\\
    f_9 & = \sin^2\theta_1 \sin 2\phi\,.&
    f_8 & = \sin 2\theta_1 \sin  \phi\,,&
    f_7 & = \sin  \theta_1 \sin  \phi\,,
\end{aligned}
\end{equation}
Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
azimuthal angle is denoted as $\phi$. The total decay width is
\begin{equation}
    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\dd q^2\,\dd k^2\,\sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
\end{equation}
As usual, we transform from a $\cos\theta_1$-dependence to a $\theta_1$-dependence.
\begin{equation}
\begin{aligned}
    P(q^2, k^2, \theta_1, \theta_2, \phi)
    & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
\end{aligned}
\end{equation}
where we also define $P_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\

@@

The physical PDF for the decay -- in the presence of Standard Model operator and their chirality flipped counter parts -- reads \cite{Boeer:2014xx}
\begin{equation}
    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, and $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads
\begin{equation}
    \begin{aligned}
% 1
        f_{1ss} & = \sin^2\theta_1 &
        f_{1cc} & = \cos^2\theta_1 &
        f_{1c}  & = \cos\theta_1\\
% 2
        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
% 3
        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\phi \\
% 4
        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\phi
    \end{aligned}
\end{equation}
The decay width reads $\langle\Gamma\rangle = \langle2 K_{1ss} + K_{1cc}\rangle$. In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
\begin{equation}
    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = K_i(q^2) / \Gamma$.

>>>>

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sense that \fred{What are the upper limits? $\pi$ or $2 \pi$? Not consistent with section I and II. I think it would be fair to talk about the dual basis already there. Do we set $f=0$ on $[\pi, 2 \pi]$?}
\begin{equation}
    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
\end{aligned}
\end{equation}

@@

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}\fred{In the theory convention. Now we use $J_i$ instead of $P_i$.}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.\fred{$\phi$ not explained}
The decay width is
\begin{equation}
    \Gamma = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = J_i(q^2) / \Gamma$.\\

@@

The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$. \fred{If this appendix includes the previous one, how come there are less angular functions here?}
Their PDFs can generally be written as \cite{Lee:1992ih}
\begin{equation}
    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
\end{equation}
where
\begin{equation}
\begin{aligned}
    f_1 & = 1\,,              &
    f_2 & = \cos 2\theta_1\,, &
    f_6 & = \cos  \theta_1\,, \\
    f_3 & = \sin^2\theta_1 \cos 2\phi\,,&
    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
    f_5 & = \sin  \theta_1 \cos  \phi\,,\\
    f_9 & = \sin^2\theta_1 \sin 2\phi\,.&
    f_8 & = \sin 2\theta_1 \sin  \phi\,,&
    f_7 & = \sin  \theta_1 \sin  \phi\,,
\end{aligned}
\end{equation}
Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
azimuthal angle is denoted as $\phi$. The total decay width is
\begin{equation}
    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\dd q^2\,\dd k^2\,\sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
\end{equation}
As usual, we transform from a $\cos\theta_1$-dependence to a $\theta_1$-dependence.
\begin{equation}
\begin{aligned}
    P(q^2, k^2, \theta_1, \theta_2, \phi)
    & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
\end{aligned}
\end{equation}
where we also define $P_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\

@@

The physical PDF for the decay -- in the presence of Standard Model operator and their chirality flipped counter parts -- reads \cite{Boeer:2014xx}
\begin{equation}
    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, and $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads \fred{cite Danny's upcoming paper}
\begin{equation}
    \begin{aligned}
% 1
        f_{1ss} & = \sin^2\theta_1 &
        f_{1cc} & = \cos^2\theta_1 &
        f_{1c}  & = \cos\theta_1\\
% 2
        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
% 3
        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\phi \\
% 4
        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\phi
    \end{aligned}
\end{equation}
The decay width reads $\langle\Gamma\rangle = \langle2 K_{1ss} + K_{1cc}\rangle$. In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
\begin{equation}
    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = K_i(q^2) / \Gamma$.
